

Communication goes by http requests, in the form of \url{\ipaddress/?key=value}.

\subsection{Request}
Currently implemented are the following parameter options.

\begin{tabular}{ll}
    \verb|panel=up| & The panels will move up until a timeout is reached, or a new up or down request is sent. \\
    \verb|panel=down| & The panels will move down under the same conditions. \\
    \verb|panel=stop| & The panels will stop moving and disable automatic mode. \\
    \verb|panel=auto| & Enable automatic mode. \\
    \verb|panel=manual| & Disable automatic mode. \\
    \verb|degrees=x| & The panels will go to $x$ degrees. \\
\end{tabular}

\subsection{Response}

The result will be in the form of json, containing the following values.

\begin{tabular}{ll}
    \verb|emergency: boolean| & Whether the system is in emergency mode or not. \\
    \verb|angle: float| & Current angle of the panels. \\
    \verb|auto_mode: boolean| & Whether the system is in automatic mode. \\
    \verb|message: string| & Human readable response message containing more information about the response, or error message in case of emergency. \\
    \verb|min_angle: float| & Lowest angle the panels can be set at. \\
    \verb|max_angle: float| & Highest angle the panels can be set at. \\
\end{tabular}

\section{Android App User Manual}\label{subsec:userManual}
To move the solar panels up (or down), press the up (or down) button and hold it until the desired position/angle is reached.
The current degree on the top right and the picture updates while the button is held, so you know when the panels are at the desired position.

To set the solar panels in auto mode, press the auto checkbox.


To set the solar panels at a certain degree, move the slider until the $x$ at the button which says "\verb|SET ANGLE AT | $x^{\circ}$" is the desired degree for the angle.
Then press the button to set the angle of the panels at that degree.
May you change your mind about the angle while the panels are moving, stop the panels with the stop button at the bottom and send a new angle request.

To update the |TextView| containing the current angle, simply press the number.
This will also update the position of the picture.
This will also check the checkbox if the panels are in auto mode, and uncheck the checkbox if the panels are not in auto mode (if needed).
