\subsection{Hardware used}\label{subsec:hardwareUsed}

The first version of the project used an Arduino.
Arduino-specific documentation that is now obsolete for this project is gathered in Section~\ref{ch:arduino}.

\subsubsection{Arduino}
We used an Arduino Nano ATmega328, bought at \href{http://nl.rs-online.com/}{rs-components}.
We used a \href{http://www.mijn-gadgets.nl/Webwinkel-Product-157562595/ENC28J60-Ethernet-Shield-Network-Module-V1.0-For-Arduino-Nano.html}{ENC28j60 Ethernet shield}, the version specifically for the nano.
This seemed easier than a wifi shield because of this reason, and with a wifi shield it seemed we needed extra components and a circuit, and we didn't really understand it.

Later when the NAS didn't want to process requests from the Arduino anymore, we bought a Micro SD Card Memory Shield Module from \url{https://www.gearbest.com/goods/pp_009462485053.html?wid=1433363&utm_source=email_sys&utm_medium=email&utm_campaign=shipping} and tried to get it to work with the ethernet shield, but that didn't work.

Then we bought a W5100 Micro SD Card Ethernet Shield from \url{https://www.gearbest.com/development-boards/pp_22810.html?wid=1433363}.
But we did not manage to get both the ethernet and the sd card to work.
Theoretically it should be possible, but in practice it seems like we want to let the Arduino do too much things together and it gets very difficult.
The test files can still be found in the UnitTests folder.

\subsubsection{Raspberry Pi}
The best solution we could think of was buying a Raspberry Pi.
As explained in Section~\ref{subsec:hardwareUsed} when the NAS stopped serving requests we decided to drop the Arduino and start using a Raspberry Pi.

There are a lot of Raspberry Pi versions, but at the moment of writing (July 2019) it seems the Raspberry Pi 4 is the most recent and complete Pi.
At the moment only the 2GB version is available.
However, since a Raspberry Pi has no analog inputs, we will need a separate Analog to Digital Converter (ADC) to read the pot meter values.
It seems that the MCP3008 is widely used, see for example \url{https://electronicshobbyists.com/raspberry-pi-analog-sensing-mcp3008-raspberry-pi-interfacing/}.
It speaks about setting 3.3v on the potmeter, just like all other places we could find, whereas we put 5v on it with the Arduino but we think it should work all the same.

%An other possibility would be to try to control the Arduino as a slave, and use the ADC of the Arduino, for example with \url{https://github.com/nanpy/nanpy} or \url{http://www.uugear.com/portfolio/raspberry-pi-measures-voltage-via-arduino/}

\subsubsection{Components list}
	\begin{itemize}
        \item Raspberry Pi 4 2GB
        \item MCP3008
        \item RJ45 breakout board
        \item JE342 ethernet connection box
        \item Adafruit Perma-Proto Full-sized Breadboard PCB
		\item BC547 NPN transistor
		\item BC557 PNP transistor
		\item $4.7$ k$\Omega$ resistor (yellow - violet - red - gold)
		\item $1$ k$\Omega$ resistor (brown - black - black - brown - brown - red)
		\item $10$ k$\Omega$ resistor (brown - black - orange - gold)
	\end{itemize}


\subsubsection{Button circuit}
	We implemented the begin- and endstops in the circuit for the buttons that move the panels up and down.
	When a button is NOT pushed, 1 and 1B, and 2 and 2B of that button are connected.
	When a button is pushed, connections are made between 1 and 1A, and 2 and 2A of that button.
	\begin{center}\begin{circuitikz}
		\draw 
		% 20, 28, E4
			(4,0) node {20} 
			(6,0) node {28}
			(8,0) node {E4}
		% button hoog
			(0.75 , -6) node {button up}
			(2.25, -5.25) node {1A}
			(2.25, -6) node {1}
			(2.25, -6.75) node {1B}
			(3.75, -5.25) node {2A}
			(3.75, -6) node {2}
			(3.75, -6.75) node {2B}
		% button laag
			(10 ,-6) node {button down}
			(7.25, -5.25) node {1A}
			(7.25,-6) node {1}
			(7.25, -6.75) node {1B}
			(8.5, -5.25) node {2A}
			(8.5, -6) node {2}
			(8.5, -6.75) node {2B}
		% drawing
			% 28 to 1,2 hoog via eindstoppen
				(6,-0.25) to (6,-1)
					to (3,-1) 
					to (3,-2)
				(2.5,-2) to (3.5,-2)
				(2.5,-2) to[switch, l_= high end stop] (2.5,-4) %eindstop hoog
					to (1.75,-4)
					to (1.75,-6) to (2,-6) 
				(3.5,-2) to[switch = low end stop] (3.5,-4) %eindstop laag
					to (4.25,-4)
					to (4.25,-6) to (4,-6) 
			% 1A hoog to 1B laag
				(2,-5.25) to (1.9,-5.25)
					to (1.9,-4.75)
					to(5.75,-4.75)
					to(5.75,-6.75)
					to(7,-6.75)
			% 2B hoog to 1A laag
				(4,-6.75) to (5.25,-6.75)
					to (5.25,-5.25)
					to (7,-5.25)
			% 20 to 1 laag
				(4,-0.25) to (4,-1.25)
					to (6.25,-1.25)
					to (6.25,-6)
					to (7,-6)
			% 1 laag to 2 laag
				(7.5,-6) to (8.25,-6)
			% E4 to 2A laag
				(8,-0.25) to (8,-4.75)
					to (9,-4.75)
					to (9,-5.25)
					to (8.75,-5.25)
		;
	\end{circuitikz}\end{center}
\subsubsection{Arduino circuit}
	\begin{center}\begin{circuitikz}
		\draw[dashed] 
			(2,10) to (5,10)
				to (5,14)
				to (2,14)
				to (2,10)
			(3.5,13) node[align=left] {Lenze\\ frequency\\ inverter}
		;
		\draw
		%E4 and its components (Arduino I/O, transistors)
			(10,0) node {E4}
			(1,1.225) node[align=center] {Arduino\\ I/O}
			(10,2) node [pnp] (pnpE4) {}
				(pnpE4.B) node[right=8mm, align=left] {Q6\\ BC557}
			(5,1.225) node [npn] (npnE4) {}
				(npnE4.B) node[right=8mm, align=left] {Q5\\ BC547}
		%Low end stop and its components
			(0.5,7.225) node[align=center] {Arduino\\ I/O}
			(10,8) node [pnp] (pnpLow) {}
				(pnpLow.B) node[right=8mm, align=left] {Q4\\ BC557}
			(4, 7.225) node [npn] (npnLow) {}
				(npnLow.B) node[right=8mm, align=left] {Q3\\ BC547}
		%High end stop and its components
			(0.5, 15.725) node[align=center] {Arduino\\ I/O}
			(10,16.5) node[pnp] (pnpHigh) {}
				(pnpHigh.B) node[right=8mm, align=left] {Q2\\ BC557}
			(4, 15.725) node[npn] (npnHigh) {}
				(npnHigh.B) node[right=8mm, align=left] {Q1\\ BC547}
		%Frequency Invertor and components (including line to GNDs)
			(3.5,11) node[sground] {}
				to (2,11)
			(1.2,11.5) node[align=left] {39 \\(GND)}
				(2,11) to[short,-*] (-1,11)
			(5.7,12) node[align=left] {28 \\ enable}
				(5,11.5) to (6.5,11.5) % fi to right
		%Arduino GND
			(-3,11) node[align=left] {Arduino\\ GND}
				(-2,11) to (-1,11)
				(-1,0) to (-1,14.955) % line on the left that connects GND
				(12,4) to (12,18.5) % line on the right that connects 20
		%circuit around E4
			(10,0.25) to (pnpE4.C)
			(pnpE4.B) to[R=R8 1k$\Omega$] (npnE4.C)
			(npnE4.E) to (5,0)
				to (-1,0)
			(npnE4.B) to[R, l=R7 4.8k$\Omega$] (2.1, 1.225)
			(9,2) node[circ] {}
				to[R,align=left, l=R9\\ 10k$\Omega$] (9,4)
				to (12,4)
			(10,4) node[circ] {} 
				to (pnpE4.E)
		%circuit around low end stop
			(pnpLow.B) to[R=R5 1k$\Omega$] (7,8) 
				to (npnLow.C)
			(9,8) node[circ] {} 
				to[R, align=left, l=R6\\ 10k$\Omega$] (9,10)
				to[short, -*] (12,10)
				(pnpLow.E) to (10,10) node[circ] {}
			(pnpLow.C) to[switch, align=left, l=low\\ end stop] (10,6)
				to (6.5,6)
				to (6.5,10) % up to high end stop
			(npnLow.B) to[R=R4 4.7k$\Omega$] (1.2, 7.225)
			(npnLow.E) to (4,6)
				to[short, -*] (-1,6)
		%circuit around high end stop
			(pnpHigh.B) to[R=R2 1k$\Omega$] (7,16.5)
				to (npnHigh.C)
			(9,16.5) to[R, align=left, l=R3\\ 10k$\Omega$, *-] (9,18.5)
				to (12,18.5)
			(pnpHigh.E) to[short, -*] (10,18.5)
			(pnpHigh.C) to (11.5,15.74) % from Q2 to right ...
			(11.5,15.74) to (11.5,7.225) % ... to right of Q4 ...
			(11.5,7.225) to[short,-*] (10,7.225) % ... to Q4
			(npnHigh.E) to (-1,14.955)
			(npnHigh.B) to[R=R1 4.7k$\Omega$] (1.2, 15.725)
			% draw end stop
			(6.5,11.5) to[switch, align=right, l=high end stop] (6.5,10)
		;
	\end{circuitikz}\end{center}

% todo docs about adc converter
% https://www.raspberrypi-spy.co.uk/2013/10/analogue-sensors-on-the-raspberry-pi-using-an-mcp3008/
	\begin{table}
		\centering
		\begin{tabular}{l|l|l|l}
			In circuit & terminal (connection to) & to meter cupboard & Raspberry Pi gpio \\
			\hline
			Ground & 4 & red/brown & GND \\
			Low end stop & no & white/green & 26 \\
			E4 & 5 & blue & 19 \\
			High end stop & 6 & green & 13 \\
			\hline
			Circuit to potmeter &&& \\
			blue (signal) & 7 & black & ? \\
			yellow/green (+5V) & 8 & yellow & +5V \\
			brown (GND) & 9 & &
		\end{tabular}
		\caption{Wiring}
		\label{tab:wiring}
	\end{table}

\subsubsection{Circuit}

The circuit schematic was created with KiCad.
To install, make sure you also install the libraries, for example on Arch install both the \verb|kicad| and \verb|kicad-library| packages.

\subsubsection{Potentiometer}
The \textbf{blue} wire from the potentiometer to the main control box is the signal wire, on connection 7 in that box.

Potmeter values as measured by the Arduino, scale 0--1024:

\begin{tabular}{ccc}
	Date & Low end stop & High end stop \\
	2017-10-22 & 360 & 74 \\
	2018-04-15 & 405 & 40 \\
	2019-08-11 & 415 & 57 \\
\end{tabular}


\subsubsection{Motor control}
We bought BC547 NPN transistors to control the 12V/20mA (\href{http://download.lenze.com/TD/8201-8204__Inverter__v02-08__EN.pdf }{docs}, page 4--11) or 14V/40mA (measured) current of the EVF8202-E frequency inverter, and also base resistors otherwise the Arduino needs to give too much current to the transistor, and the transistor will be slow to turn off because of `base charge storage'.

To control the solar panels, see Table~\ref{tab:control}, assuming you are connected as in Table~\ref{tab:wiring}.

\begin{table}
    \centering
    \begin{tabular}{llll}
        \toprule
        \textbf{Action} & \textbf{Low end stop} & \textbf{High end stop} & \textbf{E4 (direction)} \\
        \midrule
        UP & LOW & HIGH & LOW \\
        DOWN & HIGH & LOW & HIGH \\
        STOP & LOW & LOW & LOW \\
        \bottomrule
    \end{tabular}
    \caption{How to control the panels.}
    \label{tab:control}
\end{table}


\subsection{Software used}\label{subsec:softwareUsed}

We have used the \href{http://platformio.org/platformio-ide}{PlatformIO IDE}, (which uses python 2.7 and Clang for autocompletion) because it is a lot better than the standard Arduino IDE, and also seemed better than the Stino plugin for Sublime Text 3.
A plugin for CLion also looked good but we didn't get that to work.
PlatformIO worked fine for a while but not always, so as a backup you can always use the Arduino IDE, but you need to copy all the libraries from \url{SolArduino_atom\\lib} to your \url{C:\\Users\\username\\Documents\\Arduino\\libraries} (Windows) or \url{~/Arduino/Libraries} (Linux) folder.
in the Arduino IDE you need to select the board (Arduino Nano) and select the ATmega328P (Old Bootloader), if you select the new bootloader it will not work.
This was last tested in the Arduino IDE 1.8.8.